---
title: "Experiments for RQ 1"
output:
  html_document:
    df_print: paged
    number_sections: true
  html_notebook: default
  pdf_document: default
  word_document: default
---


```{r warning=FALSE}
source("../helpers.R")
knitr::opts_chunk$set(rows.print=25, cols.print=15)
# This is in inches!
tikzWidth1Col <- 3.48
```

# Research Question 1
For this question, we want to answer some statistical properties of our datasets, using descriptive statistics. Since the RQ and its facettes all relate to labelled commits, we will be using the __`jeX_L`__ dataset.

```{r}
ds <- getDataset("jeX_L")
ds <- ds[, !names(ds) %in% c("commitId", "comment")]
ds$label <- as.factor(ds$label)
ds$project <- as.factor(ds$project)

# Generate a few columns, such as "gross-size":
ds$GrossSize <- ds$NumberOfLinesAddedByAddedFiles + ds$NumberOfLinesAddedByModifiedFiles + ds$NumberOfLinesAddedByRenamedFiles + ds$NumberOfLinesDeletedByDeletedFiles + ds$NumberOfLinesDeletedByModifiedFiles + ds$NumberOfLinesDeletedByRenamedFiles

ds$NetSize <- ds$GrossSize * ds$Density

ds$GrossFiles <- ds$NumberOfFilesAdded + ds$NumberOfFilesDeleted + ds$NumberOfFilesModified + ds$NumberOfFilesRenamed
ds$NetFiles <- ds$GrossFiles * ds$AffectedFilesRatioNet
```

# Distributions of labels
```{r}
labelDist <- table(ds$label)
print(labelDist)
barplot(labelDist)
```

## Distribution of labels, per project
Let's look at the distribution of each of the A/C/P labels, and draw a chart per project.

## First Part
We are following Herraiz et al. for determining if the evolutionary patterns are the same for classifying commits, w.r.t. number of files and lines of code. We are approaching this by plotting the density of gross- and net-amount of files and gross- and net-amount of lines of code.

```{r message=FALSE, warning=FALSE}
install.packagesCond("dplyr")
library("dplyr")
install.packagesCond("plyr")
library("plyr")
install.packagesCond("ggplot2")
library("ggplot2")
install.packagesCond("tikzDevice")
library("tikzDevice")
```

```{r}
density_alpha <- 0.33
use_palette <- "Paired"

s_nf <- summary(ds$NetFiles)
mu_nf <- ddply(ds, "label", summarise, grp.mean=mean(NetFiles))
nf <- ggplot(data.frame(NetFiles=ds$NetFiles+0.1,Type=ds$label), aes(NetFiles, color=Type,fill=Type)) + geom_density(size=1,alpha=density_alpha,position="fill") + ylab("Density") + xlab("Net-Size, Files") + theme_light(base_size = 9) + scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),labels = scales::trans_format("log10", scales::math_format(10^.x))) + geom_vline(data=mu_nf, aes(xintercept=grp.mean,color=label), size=1,linetype="dashed") + scale_color_brewer(palette = use_palette) + scale_fill_brewer(palette = use_palette) + annotation_logticks(sides="b")

s_gf <- summary(ds$GrossFiles)
mu_gf <- ddply(ds, "label", summarise, grp.mean=mean(GrossFiles))
gf <- ggplot(data.frame(GrossFiles=ds$GrossFiles,Type=ds$label), aes(GrossFiles, color=Type,fill=Type)) + geom_density(size=1,alpha=density_alpha,position="fill") + ylab("Density") + xlab("Gross-Size, Files") + theme_light(base_size = 9) + scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),labels = scales::trans_format("log10", scales::math_format(10^.x))) + geom_vline(data=mu_gf, aes(xintercept=grp.mean,color=label), size=1,linetype="dashed") + scale_color_brewer(palette = use_palette) + scale_fill_brewer(palette = use_palette) + annotation_logticks(sides="b")

s_ns <- summary(ds$NetSize)
mu_ns <- ddply(ds, "label", summarise, grp.mean=mean(NetSize))
ns <- ggplot(data.frame(NetSize=ds$NetSize+0.1,Type=ds$label), aes(NetSize, color=Type,fill=Type)) + geom_density(size=1,alpha=density_alpha,position="fill") + ylab("Density") + xlab("Net-Size, LOC") + theme_light(base_size = 9) + scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),labels = scales::trans_format("log10", scales::math_format(10^.x))) + geom_vline(data=mu_ns, aes(xintercept=grp.mean,color=label), size=1,linetype="dashed") + scale_color_brewer(palette = use_palette) + scale_fill_brewer(palette = use_palette) + annotation_logticks(sides="b")

s_gs <- summary(ds$GrossSize)
mu_gs <- ddply(ds, "label", summarise, grp.mean=mean(GrossSize))
gs <- ggplot(data.frame(GrossSize=ds$GrossSize,Type=ds$label), aes(GrossSize, color=Type,fill=Type)) + geom_density(size=1,alpha=density_alpha,position="fill") + ylab("Density") + xlab("Gross-Size, LOC") + theme_light(base_size = 9) + scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),labels = scales::trans_format("log10", scales::math_format(10^.x))) + geom_vline(data=mu_gs, aes(xintercept=grp.mean,color=label), size=1,linetype="dashed") + scale_color_brewer(palette = use_palette) + scale_fill_brewer(palette = use_palette) + annotation_logticks(sides="b")

gridExtra::grid.arrange(gf, gs, nf, ns, nrow=2)

all_mus <- data.frame(
  label=sapply(mu_ns$label, function(x) paste("mean,",x)),
  gf=mu_gf$grp.mean,
  nf=mu_nf$grp.mean,
  gs=mu_gs$grp.mean,
  ns=mu_ns$grp.mean
)

print(all_mus)

all_s <- data.frame(
  type=c("Median", "Min", "Mean", "Max"),
  gf=c(s_gf[[3]], s_gf[[1]], s_gf[[4]], s_gf[[6]]),
  nf=c(s_nf[[3]], s_nf[[1]], s_nf[[4]], s_nf[[6]]),
  gs=c(s_gs[[3]], s_gs[[1]], s_gs[[4]], s_gs[[6]]),
  ns=c(s_ns[[3]], s_ns[[1]], s_ns[[4]], s_ns[[6]])
)

print(all_s)
```

```{r}
tikzDevice::tikz('density_plots.tex', width = tikzWidth1Col, height = 5)
gridExtra::grid.arrange(gf, nf, gs, ns, nrow=4)
dev.off()
```

### Same plots, but facetted
We will try and do the same 4 density plots, but using facetting.

```{r}
density_alpha <- .33
labelsFull <- list(a = "Adaptive", c = "Corrective", p = "Perfective")
dsTypes <- c("GrossFiles", "NetFiles", "GrossSize", "NetSize")
dsCombined <- data.frame(matrix(nrow = 0, ncol = 5), stringsAsFactors = FALSE)
colnames(dsCombined) <- c("value", "Type", "DsType", "Measure", "NetOrGross")

for (dsType in dsTypes) {
  netOrGross <- "Gross"
  measure <- "Files"
  if (grepl("Size$", dsType)) {
    measure <- "LOC"
  }
  
  addNetVal <- 0
  if (grepl("^Net", dsType)) {
    addNetVal <- 0.1
    netOrGross <- "Net"
  }
  temp <- data.frame(
    value = ds[[dsType]] + addNetVal,
    Type = sapply(ds$label, function(l){ return(labelsFull[[l]]) }),
    DsType = dsType,
    Measure = measure,
    NetOrGross = netOrGross
  )
  
  dsCombined <- rbind(dsCombined, temp)
}

mu_gf$Measure <- rep("Files", 3)
mu_gf$NetOrGross <- rep("Gross", 3)
mu_nf$Measure <- rep("Files", 3)
mu_nf$NetOrGross <- rep("Net", 3)
mu_gs$Measure <- rep("Size", 3)
mu_gs$NetOrGross <- rep("Gross", 3)
mu_ns$Measure <- rep("Size", 3)
mu_ns$NetOrGross <- rep("Net", 3)

musCombined <- rbind(mu_gf, mu_gs, mu_nf, mu_ns)
musCombined$Type <- sapply(musCombined$label, function(l){ return(labelsFull[[l]]) })
musCombined$DsType <- paste(musCombined$NetOrGross, musCombined$Measure, sep = "")


densPlot2 <- ggplot(dsCombined, aes(x = value, color = Type, fill = Type)) +
  geom_density(size = 1, alpha = density_alpha, position = "fill") +
  theme_light(base_size = 9) +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  geom_vline(
    data=filter(musCombined),
    aes(xintercept = grp.mean, color = Type), size = 1, linetype = "dashed"
  ) +
  xlab("Amount of Files/LOC") + ylab("Stacked density per maintenance activity") +
  scale_color_brewer(palette = use_palette) +
  scale_fill_brewer(palette = use_palette) +
  annotation_logticks(sides="b") +
  facet_wrap(
    DsType ~., scales = "free_x", ncol = 1,
    labeller = labeller(DsType = c(
      "GrossFiles" = "Files, gross", "GrossSize" = "LOC, gross",
      "NetFiles" = "Files, net", "NetSize" = "LOC, net"))
  ) +
  theme(
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black"),
    legend.position = "bottom",
    axis.title.y.left = element_text(margin = margin(r=15)),
    axis.title.x.bottom = element_text(margin = margin(t=10)),
    legend.title = element_blank(),
    legend.text = element_text(margin = margin(r = 1, unit = "picas"))
  )

densPlot2
```
#### As Tikz
```{r}
tikzDevice::tikz('density_plots2.tex', width = tikzWidth1Col, height = 5.5)
densPlot2
dev.off()
```

From these analyses, we can draw the following conclusions. First of all, the distributions of amount of files and lines of code is very similar, when comparing gross with its respective net, when compared to size of at least one line. As expected, the minimum values for gross values (i.e., lines or files) are $1$ (as a commit cannot comprise an empty set of changes), whereas the net-values can, and are, in fact be $0$. That explains why we can observe significant amounts of commits, that do not have any files or lines affected, especially for the corrective and perfective labels.

```{r}
sizes <- c("label", "GrossFiles", "NetFiles", "GrossSize", "NetSize")
labels <- c("a", "c", "p")
probTable <- data.frame(
  matrix(ncol = length(sizes), nrow = 0), stringsAsFactors = FALSE)

for (l in labels) {
  
  row1 <- list()
  row2 <- list()
  row3 <- list()
  
  for (s in sizes[2:length(sizes)]) {
    e <- ecdf(ds[s][ds["label"] == l] + 0.1)
    
    row1[["label"]] <- paste(l, "[0,1)", sep = ", ")
    row2[["label"]] <- paste(l, "[1,2)", sep = ", ")
    row3[["label"]] <- paste(l, "[2,5)", sep = ", ")
    
    row1[[s]] <- e(1 - 1e-12)
    row2[[s]] <- e(2 - 1e-12) - e(1 - 1e-12)
    row3[[s]] <- e(5 - 1e-12) - e(1 - 1e-12)
  }
  
  probTable <- rbind(probTable, row1)
  probTable$label <- as.character(probTable$label)
  probTable <- rbind(probTable, row2)
  probTable <- rbind(probTable, row3)
}

print(probTable)
```

```{r}
print(cor(ds$NetFiles, ds$NetSize))
print(cor(ds$GrossFiles, ds$GrossSize))
```



## Part B
Every tenth commit is a small change (i.e. only one line affected). Are net-size commits increasing this percentage? We will use the ECDF of the entire dataset to find out whether this is true.

Here we will check what the probabiltiy of a certain kind of commit in a certain size-range is.
```{r}
size <- nrow(ds)
ranges <- c(0, 1, 2, 3, 4, 5, 8, 10, 15, 25, 50, 75, 100, 200, 500, 1000, 3000, 10000, 25000, 50000, 100000)

ecdfNet <- ecdf(ds$NetSize)
ecdfGro <- ecdf(ds$GrossSize)

ecdfTable <- data.frame(
  matrix(ncol = 5, nrow = 0), stringsAsFactors = FALSE)


for (r in ranges) {
  tNet <- table(ds[ds$NetSize <= r,]["label"])
  tNet <- tNet / ifelse(sum(tNet) == 0, 1, sum(tNet)) # normalize percentages
  tGro <- table(ds[ds$GrossSize <= r,]["label"])
  tGro <- tGro / ifelse(sum(tGro) == 0, 1, sum(tGro))
  
  for (l in labels) {
    newRow <- list(
      type = paste(l, "<=", r, sep = ", "),
      max = r,
      label = l
    )
    newRow[["net"]] <- tNet[[l]]
    newRow[["gro"]] <- tGro[[l]]
    
    ecdfTable <- rbind(ecdfTable, newRow)
    ecdfTable$type <- as.character(ecdfTable$type)
    ecdfTable$label <- as.character(ecdfTable$label)
  }
}

print(ecdfTable)

# Now let's plot them:
temp <- ecdfTable[order(ecdfTable$label, ecdfTable$max), ]

density_alpha <- 0.5

gro_et <- ggplot(temp, aes(x=as.factor(temp$max))) + geom_bar(aes(fill=label, weight=gro), alpha = density_alpha, width = .85) + theme_light(base_size = 9) + scale_fill_brewer(palette = use_palette) + ylab("Ratio") + xlab("Gross-size, LOC, $ecdf(x)$") + labs(fill="Type") + theme(axis.text.x = element_text(angle = 90, vjust = .4)) + scale_x_discrete(labels = function(n){format(as.numeric(n), digits = 0, big.mark = ",")})

net_et <- ggplot(temp, aes(x=as.factor(temp$max))) + geom_bar(aes(fill=label, weight=net), alpha = density_alpha, width = .85) + theme_light(base_size = 9) + scale_fill_brewer(palette = use_palette) + ylab("Ratio") + xlab("Net-size, LOC, $ecdf(x)$") + labs(fill="Type") + theme(axis.text.x = element_text(angle = 90, vjust = .4)) + scale_x_discrete(labels = function(n){format(as.numeric(n), digits = 0, big.mark = ",")})

gridExtra::grid.arrange(gro_et, net_et, nrow=2)
```
```{r}
tikzDevice::tikz('ecdf_ratio_per_label.tex', width = 3.8, height = 2.6)
gridExtra::grid.arrange(gro_et, net_et, nrow=2)
dev.off()
```


### Plot the same, but facetted
```{r}
library(data.table)
tempXnetGross <- copy(temp)
tempXnetGross$Value <- temp$net
tempXnetGross$DsType <- rep("Net", nrow(temp))
ecdfRatioCombined <- rbind(tempXnetGross)

tempXnetGross <- copy(temp)
tempXnetGross$Value <- temp$gro
tempXnetGross$DsType <- rep("Gross", nrow(temp))
ecdfRatioCombined <- rbind(ecdfRatioCombined, tempXnetGross)

ecdfRatioCombined$max <- as.factor(ecdfRatioCombined$max)

labelsFull <- list(a = "Adaptive", c = "Corrective", p = "Perfective")
ecdfRatioCombined$label <- sapply(ecdfRatioCombined$label, function(l){ return(labelsFull[[l]]) })
ecdfRatioCombinedXLabs <- c("Gross" = "Gross-size, LOC, $\\textit{ecdf(x)}$", Net = "Net-size, LOC, $\\textit{ecdf(x)}$")

saveRDS(ecdfRatioCombined, "ecdfRatioCombined.rds")
saveRDS(ecdfRatioCombinedXLabs, "ecdfRatioCombinedXLabs.rds")
```

```{r}
density_alpha <- .5
ecdfRatioCombined <- readRDS("ecdfRatioCombined.rds")
ecdfRatioCombinedXLabs <- readRDS("ecdfRatioCombinedXLabs.rds")

ecdfRatioPerLab2 <- ggplot(ecdfRatioCombined, aes(x = max)) +
  geom_bar(aes(fill=label, weight=Value), alpha = density_alpha, width = .85) +
  theme_light(base_size = 9) +
  scale_fill_brewer(palette = use_palette) +
  ylab("Cumulative ratio per activity") +
  xlab("Lines of code") +
  labs(fill="Type") +
  theme(axis.text.x = element_text(angle = 60, vjust = .4)) +
  scale_x_discrete(labels = function(n){format(as.numeric(n), digits = 0, big.mark = ",")}) +
  facet_wrap(. ~ DsType, nrow = 2, labeller = labeller(DsType = ecdfRatioCombinedXLabs)) +
  theme(
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black"),
    legend.position = "bottom",
    axis.title.y.left = element_text(margin = margin(r=15)),
    axis.title.x.bottom = element_text(margin = margin(t=10)),
    legend.title = element_blank(),
    legend.text = element_text(margin = margin(r = 1, unit = "picas"))
  )

ecdfRatioPerLab2
```

#### As Tikz
```{r}
tikzDevice::tikz('ecdf_ratio_per_label2.tex', width = tikzWidth1Col, height = 3.4)
ecdfRatioPerLab2
dev.off()
```

Also, let's check the distribution of commits within specific ranges, regardless of their label:

```{r}
percTable <- data.frame(
  matrix(ncol = 5, nrow = 0), stringsAsFactors = F)

for (r in ranges) {
  tNet <- table(ds[ds$NetSize <= r,]["label"])
  tGro <- table(ds[ds$GrossSize <= r,]["label"])
  
  newRow <- list(
    type = paste("all", "<=", r, sep = ", "),
    max = r,
    net = sum(tNet) / size,
    gro = sum(tGro) / size
  )
  
  percTable <- rbind(percTable, newRow)
  percTable$type <- as.character(percTable$type)
}

print(percTable)
```

Now let's print these two series as well:

```{r}
temp <- percTable[order(percTable$max), ]
temp <- temp[temp$net < 1-1e-4, ]

temp1 <- data.frame(
  max = rep(temp$max, each=2),
  Type = rep(c("Net", "Gross"), nrow(temp)),
  value = as.vector(rbind(temp$net, temp$gro))
)

density_alpha <- 0.66

ratioRangeComm <- ggplot(temp1, aes(fill=Type, y=value, x=as.factor(temp1$max))) +
  geom_bar(position = "dodge", stat = "identity", alpha = density_alpha) +
  theme_light(base_size = 9) +
  xlab("Size, LOC, $\\textit{ecdf(x)}$") +
  ylab("Ratio") +
  scale_fill_brewer(palette="Paired") +
  scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1)) +
  theme(
    axis.title.y.left = element_text(margin = margin(r=15)),
    axis.title.x.bottom = element_text(margin = margin(t=10)),
    legend.title = element_blank(),
    legend.text = element_text(margin = margin(r = 1, unit = "picas")),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, vjust = .4)
  ) +
  scale_x_discrete(labels = function(n){format(as.numeric(n), digits = 0, big.mark = ",")})

ratioRangeComm
```

```{r}
tikzDevice::tikz('ratio_range_commit.tex', width = tikzWidth1Col, height = 2.4)
ratioRangeComm
dev.off()
```


# Addendum
While we show differences between net- and gross-size, it is probably worth it show how significant this is on average. Therefore, we want to plot all net- vs. all gross-sizes of all commits we have analyzed during this project (short of 360k).

```{r}
gex_sizes <- getDataset("rq1_g_vs_n", removeUnwantedColums = F)
#gex_sizes <- gex_sizes[gex_sizes$SizeGross > 0 & gex_sizes$SizeGross < 25e3, ]
# Convert from Integer64 to double
gex_sizes$SizeNet <- as.numeric(gex_sizes$SizeNet)
gex_sizes$SizeGross <- as.numeric(gex_sizes$SizeGross)
gex_num <- nrow(gex_sizes)
# Commits with size 0 or equal net/gross:
gex_num_size_0 <- sum(gex_sizes$SizeGross == 0)
gex_num_size_same <- sum(gex_sizes$SizeGross == gex_sizes$SizeNet) - gex_num_size_0
# Remove those where SizeGross is 0
gex_sizes <- gex_sizes[gex_sizes$SizeGross > 0, ]
# Those commits with Density=1:
gex_sizes_dens_1 <- gex_sizes[gex_sizes$SizeNet == gex_sizes$SizeGross, ]
# Then remove those with Density=1:
gex_sizes <- gex_sizes[gex_sizes$SizeNet < gex_sizes$SizeGross, ]
# Remove those where equal size:
# Calculate the Density:
gex_sizes$Density <- gex_sizes$SizeNet / gex_sizes$SizeGross
gex_sizes_dens_1$Density <- 1
```

Out of `r gex_num` commits, `r gex_num_size_0` had a size of zero (gross and net), and another `r gex_num_size_same` had equal counts of lines affected gross/net (i.e., those had a Density of 1). The remaining amount of commits with a density between in the range $[0, 1)$ is `r nrow(gex_sizes)`, which is `r round(100 * nrow(gex_sizes) / gex_num, 2)` % of all commits. The average amount of lines gross is `r mean(gex_sizes$SizeGross)`, for net it is `r mean(gex_sizes$SizeNet)`. The correlation between net and gross is `r cor(gex_sizes["SizeGross"], gex_sizes["SizeNet"])`. We get about 1% of empty commits, those are due to, e.g., starting or stopping to track files that are yet empty, or changes in binary files that result in no lines changed.

Let's plot these (all gross > 0 and gross != net):
* Boxplot gross vs. net sizes
* ecdf of Density
* 2d density of Gross-size vs. Density

```{r}
density_alpha <- .66
temp <- data.frame(
  Size = c(gex_sizes$SizeGross + .1, gex_sizes$SizeNet + .1),
  Type = c(rep("LOC, gross", nrow(gex_sizes)), rep("LOC, net", nrow(gex_sizes)))
)
tempMeans <- aggregate(Size ~ Type, temp, mean)
tempMeans$Size <- round(tempMeans$Size)
tempMeans$SizeLab <- paste("\\footnotesize{mean: $", tempMeans$Size, "$}", sep = "")
tempMedians <- aggregate(Size ~ Type, temp, median)
tempMedians$Size <- round(tempMedians$Size)
tempMedians$SizeLab <- paste("\\footnotesize{median: $", tempMedians$Size, "$}", sep = "")
set.seed(1337)
tempJitter <- temp[sample(rownames(temp), 800), ] # limit for the plots!

bp <- ggplot(temp[sample(rownames(temp), 2e4), ], aes(x=Type, y=Size, color=Type)) +
    #geom_boxplot(aes(fill = Type), alpha = density_alpha) +
    geom_violin(aes(fill = Type), alpha = density_alpha) +
    facet_wrap(Type ~., scales = "free_x") + # This will eliminate empty cols
    scale_color_brewer(palette = "Paired") +
    scale_fill_brewer(palette = "Paired") +
    theme_light(base_size = 9) +
    #geom_jitter(data=tempJitter, shape=21, position = position_jitter(0.35)) +
    geom_hline(data=tempMeans, aes(yintercept=Size), color="#666666") +
    geom_label(
      data=tempMeans,
      aes(y=Size, label=SizeLab),
      fill="#ffffffbb", color="black", hjust=.1
    ) +
    geom_hline(data=tempMedians, aes(yintercept=Size), color="#333333") +
    geom_label(
      data=tempMedians,
      aes(y=Size, label=SizeLab),
      fill="#ffffffbb", color="black", hjust=.1
    ) +
    xlab(element_blank()) +
    ylab("Size of Commits in LOC") +
    labs(fill = "Type", color = "Type") +
    scale_y_log10(
      breaks = c(.1, 1, 1e1, 1e2, 1e3, 1e4, 1e5, 1e6),
      labels = c("0", sapply(c(0,1,2,3,4,5,6), function(x) paste("$10^{", x, "}$", sep = "")))
      #breaks = scales::trans_breaks("log10", function(x) 10^x),
      #labels = scales::trans_format("log10", function(x) paste("$10^{", x, "}$", sep = ""))
    ) +
    theme(legend.position = "none",
          strip.background = element_rect(fill="#dfdfdf"),
          strip.text = element_text(color="black"),
          axis.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y.left = element_text(margin = margin(r=15)))
bp
```
```{r}
# As Tikz:
tikzDevice::tikz('density_net-vs-gross.tex', width = tikzWidth1Col, height = 2.5)
bp
dev.off()
```

Let's print the ECDF of the Density, once with the density=1 commits, and once without.

```{r}
set.seed(43215)
numSamples <- 3500
numSamplesD1 <- round(numSamples) / nrow(gex_sizes) * nrow(gex_sizes_dens_1)

temp <- data.frame(
  Density = c(
    rbind(
      gex_sizes[sample(rownames(gex_sizes), numSamples), ],
      gex_sizes_dens_1[1:numSamplesD1, ]
    )$Density,
    gex_sizes[sample(rownames(gex_sizes), numSamples), ]$Density),
  IncD1 = factor(c(
    rep("$0 \\leq \\textit{Density} < 1$", numSamples),
    rep("$0 \\leq \\textit{Density} \\leq 1$", numSamples + numSamplesD1)
  ), levels = c("$0 \\leq \\textit{Density} < 1$", "$0 \\leq \\textit{Density} \\leq 1$"), ordered = T)
)

ecdfPlot <- ggplot(temp, aes(x=Density, fill=IncD1)) +
  stat_ecdf(aes(ymin=0, ymax=..y..), geom = "ribbon", alpha = 0.33) +
  stat_ecdf(geom = "step") +
  ylab("$\\textit{ecdf(\\small{Density})}$") +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  scale_x_continuous(breaks = seq(0, 1, by = .1), labels = sapply(seq(0, 1, by = .1), function(x) format(x, nsmall=1))) +
  scale_y_continuous(breaks = seq(0, 1, by = .1), labels = sapply(seq(0, 1, by = .1), function(x) format(x, nsmall=1))) +
  theme_light(base_size = 9) +
  xlab("Commit Density") +
  theme(legend.position = "none",
        strip.background = element_rect(fill="#dfdfdf"),
        strip.text = element_text(color="black"),
        axis.text.x = element_text(angle = 60, vjust = .4),
        axis.title.y.left = element_text(margin = margin(r=15)),
        axis.title.x.bottom = element_text(margin = margin(t=10))) +
  facet_wrap(IncD1 ~., ncol = 2)

ecdfPlot
```

```{r}
# As Tikz:
tikzDevice::tikz('density_ecdf.tex', width = tikzWidth1Col, height = 2.1)
ecdfPlot
dev.off()
```


The 2D density does not work well, we will create quantiles of the data and plot the density of Density for each.

```{r}
temp <- rbind(gex_sizes)#, gex_sizes_dens_1) # We do those extra!
qs <- sort(quantile(temp$SizeGross, probs = c(seq(.125,.999,by=.125), .95)))
temp <- data.frame()
tempAgg <- data.frame()
useLabOrdered <- c()

for (i in 1:(1 + length(qs))) {
  filtered <- NULL
  useLab <- NULL
  if (i == 1) {
    filtered <- gex_sizes[gex_sizes$SizeGross <= qs[[i]], ]
    #useLab <- paste("$\\textit{LOC} \\leq$", qs[[i]])
    useLab <- paste("$\\left[0 ; ", qs[[i]], "\\right]$")
  } else if (i == 1 + length(qs)) {
    filtered <- gex_sizes[gex_sizes$SizeGross > qs[[i - 1]], ]
    useLab <- paste("$\\left(", format(qs[[i - 1]], big.mark = ","), "; \\infty \\right]$")
  } else {
    filtered <- gex_sizes[gex_sizes$SizeGross > qs[[i - 1]] & gex_sizes$SizeGross <= qs[[i]], ]
    useLab <- paste("$\\left(", format(qs[[i - 1]], big.mark = ","), ";", format(qs[[i]], big.mark = ","), "\\right]$")
  }
  
  #filtered$Q <- ifelse(i == 1 + length(qs), "100ยง", gsub("%", "ยง", names(qs)[i]))
  filtered$Q <- useLab
  useLabOrdered <- c(useLabOrdered, useLab)
  
  temp <- rbind(temp, filtered)
  temp$Q <- as.character(temp$Q)
  
  tempAgg <- rbind(tempAgg, data.frame(
    mean = mean(filtered$Density),
    median = median(filtered$Density),
    max = max(filtered$Density),
    min = min(filtered$Density),
    Q = useLab
  ))
  tempAgg$Q <- as.character(tempAgg$Q)
}

#temp$Q <- factor(temp$Q, levels = c(tail(sort(unique(temp$Q)), -1), "100ยง"), ordered = T)
#temp$Q <- as.factor(temp$Q)
temp$Q <- factor(temp$Q, useLabOrdered, ordered = T)
qs
```
```{r}
ggplot(temp, aes(Density, color=Q, fill=Q)) + geom_density(alpha=.5) +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  facet_wrap(Q ~ .) +
  xlab("Commit-Density") +
  ylab("Statistical density") +
  labs(fill="Quantile", color="Quantile") +
  theme_light(base_size = 9) +
  theme(#legend.position = "bottom",
        strip.background = element_rect(fill="#dfdfdf"),
        strip.text = element_text(color="black"),
        axis.title.y.left = element_text(margin = margin(r=15)),
        axis.title.x.bottom = element_text(margin = margin(t=10)))
```

```{r}
library(ggridges)

ridgePlot <- ggplot(temp, aes(x = Density, y = Q, fill = Q)) +
  scale_color_brewer(palette = "Paired") +
  scale_fill_brewer(palette = "Paired") +
  geom_density_ridges(alpha = .33) +
  labs(fill="Quantile", color="Quantile") +
  xlab("Commit Density") +
  ylab("Relative Likelihood") +
  labs(fill = "Commit Size\nin LOC (range)") +
  theme_light(base_size = 9) +
  theme(axis.text.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_text(margin = margin(t=-23, r=2.5)),
        legend.text = element_text(margin = margin(r=0)),
        axis.title.x.bottom = element_text(margin = margin(t=10))) +
  guides(fill=guide_legend(nrow=4, byrow = T))

ridgePlot
```

```{r}
tikzDevice::tikz('density_in_quantiles.tex', width = tikzWidth1Col, height = 3.5)
ridgePlot
dev.off()
```

The last part is to show (Density=1)-commits' distribution

```{r}
dens1Plot <- ggplot(gex_sizes_dens_1, aes(SizeGross, fill="")) +
  geom_density(alpha=.33, size=1) +
  scale_x_log10(
    limits = c(1, 10^2.5),
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", function(x) paste("$10^{", x, "}$", sep = ""))
  ) +
  scale_color_brewer(palette = use_palette) +
  scale_fill_brewer(palette = use_palette) +
  annotation_logticks(sides="b") +
  ylab("Relative Likelihood") +
  xlab("Gross Commit size in LOC") +
  theme_light(base_size = 9) +
  theme(legend.position = "none",
        axis.title.x.bottom = element_text(margin = margin(t=10)),
        axis.title.y.left = element_text(margin = margin(r=15)))

dens1Plot
```


```{r}
tikzDevice::tikz('density_1_density.tex', width = tikzWidth1Col, height = 2)
dens1Plot
dev.off()
```


# Density stacked bar-charts
We were asked to explain the density better. We create a stacked bar-chart for this purpose, demonstrating net- vs. gross-size (and everything contributing to it).

```{r}
densFactor <- factor(c(), levels = c("Detailed", "All"), ordered = T)
densTypeFactor <- factor(c(), levels = c("Gross size", "Net-Functionality", "Clones", "Dead code", "Whitespace", "Comments"), ordered = T)

densBarData <- data.frame(
  Bar = factor(c(rep("Detailed", 6), rep("All", 6)), levels = levels(densFactor)),
  Type = factor(rep(c("Gross size", "Clones", "Dead code", "Whitespace", "Comments", "Net-Functionality"), 2), levels = levels(densTypeFactor)),
  LOC = c(205, rep(0, 5), 0, 45, 20, 55, 35, 50)
)

densBarPlot <- ggplot(densBarData, aes(fill=Type, y=LOC, x=Bar)) +
  ylab("Lines of Code") +
  xlab("") +
  geom_bar(position = "stack", stat="identity") +
  scale_color_brewer(palette = use_palette) +
  scale_fill_brewer(palette = use_palette) +
  theme_light(base_size = 9) +
  theme(axis.text.x = element_blank(),
        legend.title = element_text(margin = margin(b=10)),
        axis.title.x.bottom = element_blank(),
        axis.title.y.left = element_text(margin = margin(r=15)))

densBarPlot
```

```{r}
tikzDevice::tikz('density_barplots.tex', width = 3.48, height = 2.2)
densBarPlot
dev.off()
```








































